The \dealii Library, Version 9.2

### 2020-05-11 9.2/paper.tex
update list of contributors

%\renewcommand{\baselinestretch}{2.0}

@@

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
%     Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

% %
% \author[8]{Luca~Heltai}
% \affil[8]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
%   {\texttt{luca.heltai@sissa.it}}}
%
 \author[9]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch@lnm.mw.tum.de}}}
%
% \author[10]{Ross~Maguire~Kynch}
% \affil[10]{Zienkiewicz Centre for Computational Engineering,
%   College of Engineering, Swansea University,
%   Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
%   {\texttt{rkynch@gmail.com}}}
%
\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

  \author[9,13]{Peter Munch}

 \affil[13]{Institute of Materials Research, Materials Mechanics, 
 Helmholtz-Zentrum Geesthacht, 
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

%
% \author[4]{Jean-Paul~Pelteret}
%
% \author[*1]{Bruno~Turcksin}
%
% \author[12]{David Wells}
% \affil[12]{Department of Mathematics, University of North Carolina,
%   Chapel Hill, NC 27516, USA.
%   {\texttt{drwells@email.unc.edu}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved large-scale performance}
\label{subsec:performance}

Large-scale simulations with 304,128 cores have revealed bottlenecks in release 
9.1 during initialization due to the usage of expensive collective operations 
like \texttt{MPI\_Allgather()} and \texttt{MPI\_\allowbreak Alltoall()}, e.g., during the 
pre-computationof the index ranges of all processes, which have been stored in  an array. 
This information is needed to set up 
the  \texttt{Utilities::MPI::Par\-ti\-ti\-oner} class. 
In release 9.2, we have removed such arrays and have replaced 
the \texttt{MPI\_Allgather}/\allowbreak\texttt{MPI\_\allowbreak Alltoall} 
function calls by consensus algorithms~\cite{hoefler2010scalable}, which can be 
found in the namespace \texttt{Utilities::\allowbreak MPI::\allowbreak ConsensusAlgorithms} (short: \texttt{CA}): now, only the locally relevant information about the index ranges is (re)computed when needed, using these algorithms. 
We provide two flavors of the consensus algorithm: the two-step 
approach \texttt{CA::PEX} and the \texttt{CA::NBX}, 
which uses only point-to-point communications and a single \texttt{MPI\_IBarrier()}.

%Consensus algorithms are algorithms dedicated to efficient dynamic-sparse 
%communication patterns. In this context, the term ``dynamic-sparse'' means 
%that by the time this function is called, the other processes do not know 
%yet that they have to answer requests and
%each process only has to communicate with a small subset of processes of the 
%MPI communicator. We provide two flavors of the consensus algorithm: the two-step 
%approach \texttt{ConsensusAlgorithms::PEX} and the \texttt{ConsensusAlgorithms::NBX}, 
%which uses only point-to-point communications and a single \texttt{MPI\_IBarrier()}. 
%The class \texttt{ConsensusAlgorithms::Selector} selects one of the two previous 
%algorithms, depending on the number of processes.

Users can use the new algorithms for their own dynamic-sparse problems by 
providing a list of target 
processes and pack/unpack routines either by implementing the interface 
\texttt{CA::\allowbreak Process} or by providing \texttt{std::function} 
objects to \texttt{CA::AnonymousProcess}.

By replacing the collective communications during setup and removing the arrays 
that contain information for each process (enabled by the application of consensus 
algorithms and other modifications---a full list of modifications leading to this 
improvement can be found online), we were able to significantly improve the setup 
time for large-scale simulations and to solve a Poisson problem with multigrid 
with 12T unknowns. 
Figure~\ref{} compares the timings of a simulation (incl. setup) with the 
previous release 9.1 and with the current release 9.2. 
{\color{red}TODO[Peter/Martin] description of the results}

The new code has been also applied to solve problems with adaptively refined 
meshes with more than 4B unknowns. {\color{red}TODO[Timo]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A new fully distributed triangulation class}
\label{subsec:pft}

By release 9.1, all triangulation classes of \texttt{deal.II} have in common that the coarse grid is shared by 
all processes and the actual mesh used for computations is constructed by repeated 
refinement. However, this has its limitations in industrial applications where, often, the mesh comes 
from an external mesh generator in the form of a file that already contains millions 
or tens of millions of cells. For such configurations, applications might already 
run out of  main memory while reading the complete mesh by each MPI process.

The new class \texttt{parallel::fullydistributed::Triangulation} targets this issue 
by distributing also the coarse grid. Such 
a triangulation can be created by providing a \texttt{Triangulation\-De\-scrip\-tion::Description} struct to each process, containing 
1) the relevant data to construct the local part of the coarse grid, 2) the 
translation of the local coarse-cell IDs to globally unique IDs, 3) the hierarchy 
of mesh refinements, and 4) the owner of the cells on the active mesh level as well 
as on the multigrid levels. Once the triangulation is set up with this struct, no adaptive
changes to the mesh are allowed at the moment.

%The \texttt{TriangulationDescription::Description} struct can be filled manually or 
%by the utility functions from the \texttt{TriangulationDescription::Utilities} 
%namespace. The function \texttt{create\_\allowbreak description\_\allowbreak 
%from\_ \allowbreak triangulation()} can convert a base triangulation (partitioned 
%serial \texttt{Tri\-angulation} and \texttt{parallel::distributed::Triangulation}) 
%to such a struct. The advantage of this approach is that all known utility 
%functions from the namespaces \texttt{GridIn} and \texttt{GridTools} can be used 
%on the base triangulations before converting them to the structs. Since this 
%function suffers from the same main memory problems as described above, we also 
%provide the function \texttt{create\_description\_from\_triangulation\_in\_groups()}, 
%which creates the structs only on the master process in a process group. These 
%structs are filled one by one and are sent to the relevant processes once they are 
%ready. A sensible process group size might contain all processes of one compute node.

The new (fully) distributed triangulation class works---in contrast to  
\texttt{parallel::distributed::\allowbreak Tri\-an\-gu\-la\-tion}---not only for 2D- and 3D- but also for 
1D-problems. It can be used in the context of geometric multigrid methods and 
supports periodic boundary conditions. Furthermore, hanging nodes are supported.

%We intend to extend the usability of the new triangulation class in regard of 
%different aspects, e.g., I/O. In addition, we would like to enable adaptive mesh 
%refinement, a feature of the other triangulation classes, which is very much 
%appreciated by many users. For repartitioning, we plan to use an oracle approach 
%known from \texttt{parallel::distributed::Triangulation}. Here, we would like to 
%rely on a user-provided partitioner, which might also be a graph partitioner.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances of the SIMD capabilities and the matrix-free infrastructure}
\label{subsec:mf}

%\begin{itemize}
%\item ECL
%\item VectorizedArrayType
%\end{itemize}

The class \texttt{VectorizedArray<Number>} is a key ingredient for the high 
node-level performance of the matrix-free algorithms in deal.II~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper 
class around $n$ vector entries of type \texttt{Number} and delegates relevant 
function calls to appropriate Intrinsics instructions. Up to release 9.1, the 
vector length $n$ has been set at compile time of the library to the highest 
possible value supported by the given processor architecture.

The class \texttt{VectorizedArray} has been made more user-friendly by making 
it compatible with the STL algorithms found in the header \texttt{<algorithm>}. 
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}. 
Furthermore, the \texttt{VectorizedArray} class supports range-based iterations over its entries and, i.a., the following 
algorithms: \texttt{std::\allowbreak ad\-vance()}, \texttt{std::distance()}, and \texttt{std::max\_element()}.

It has been also extended with the second optional template argument 
\texttt{VectorizedArray<Number, size>} with \texttt{size} being related to the 
vector length, i.e., the number of lanes to be used and the instruction set to be 
used. By default, the number is set to the highest value supported by the given 
hardware. A full list of supported 
vector lengths are presented in Table~\ref{tab:vectorizedarray}.

All matrix-free related classes (like \texttt{MatrixFree} and \texttt{FEEvaluation}) 
have been templated with the floating-point number type \texttt{Number} (e.g. \texttt{double} or \texttt{float}); the computations were performed implicitly 
on \texttt{VectorizedArray<Number>} structs with the highest 
instruction-set-architecture extension, with each lane responsible for a separate 
cell (vectoriziation over elements). In release 9.2, all matrix-free classes 
have been extended with a new optional template argument specifying the 
\texttt{VectorizedArrayType}. This allows users to select the vector length/ISA and, 
as a consequence, the number of cells to be processed at once directly in their applications: 
The deal.II-based 
library \texttt{hyper.deal}~\cite{munch2020hyperdeal}, which solves the 6D Vlasov--Poisson equation with high-order 
discontinuous Galerkin methods (with more than 1024 degrees of freedom per cell), works with \texttt{MatrixFree} objects of different SIMD-vector 
length in the same application and benefits---in terms of performance---by the possibility of decreasing the number of cells processed by a single SIMD instruction.

\begin{table}
\caption{Supported vector lengths of the class \texttt{VectorizedArray} and 
the corresponding instruction-set-architecture extensions. }\label{tab:vectorizedarray}
\centering
\begin{tabular}{ccc}
\toprule
\textbf{double} & \textbf{float} & \textbf{ISA}\\
\midrule
VectorizedArray<double, 1> & VectorizedArray<float, 1> & (auto-vectorization) \\
VectorizedArray<double, 2> & VectorizedArray<float, 4> & SSE2 \\ 
VectorizedArray<double, 4> & VectorizedArray<float, 8> & AVX/AVX2 \\ 
VectorizedArray<double, 8> & VectorizedArray<float, 16> & AVX-512 \\ 
\bottomrule
\end{tabular}

\caption{Comparison of relevant SIMD-related classes in deal.II and C++20.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (C++20)} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

A side effect of introducing the new template argument \texttt{VectorizedArrayType} 
in the \texttt{MatrixFree} classes is that any data structures 
\texttt{VectorizedArrayType} can be processed if they support required 
functionalities like \texttt{size()} or \texttt{value\_type}. In this context, we 
would like to highlight that the new \texttt{C++20} feature \texttt{std::simd} 
can be processed by the matrix-free infrastructure with minor internal 
adjustment as an open pull request shows 
(see \url{https://github.com/dealii/dealii/pull/9994}).  
Table~\ref{tab:simd} gives a comparison of the deal.II-specific SIMD classes and 
the equivalent C++20 classes. 
%We welcome the standardization of the SIMD 
%parallelization paradigm in C++ and intend to replace step by step our own 
%wrapper class, which has been continuously developed over the last decade. We 
%would like to emphasize that the work invested in this class was not in vain, 
%since many performance-relevant utility functions implemented with \texttt{VectorizedArray} in mind (e.g., \texttt{vectorized\_load\_and\_transpose} 
%and \texttt{vectorized\_transpose\_and\_store}) will be still used, since they 
%have not become part of the standard.

%Further additions to the \texttt{MatrixFree} infrastructure consist of:
%\begin{itemize}
%\item a new variant of \texttt{MatrixFree::cell\_loop()}: It takes two
%\texttt{std::function} objects with ranges on the locally owned degrees of freedom, one
%with work to be scheduled before the cell operation first touches some
%unknowns and another with work to be executed after the cell operation last 
%touches them. The goal of
%these functions is to bring vector operations close to the time when the
%vector entries are accessed by the cell operation, which increases the cache
%hit rate of modern processors by improved temporal locality. 
%\item a new form of loop \texttt{MatrixFree::loop\_cell\_centric()}: This 
%kind of loop can be used in the context of discontinuous Galerkin methods, 
%where both cell and face integrals have to be evaluated. While in the case of 
%the traditional \texttt{loop}, cell and face integrals have been performed 
%independently, the new loop performs all cell and face integrals of a cell in 
%one go. This includes that each face integral has to be evaluated twice, but 
%entries have to be written into the solution vector only once with improved 
%data locality. Previous publications based on \texttt{deal.II} have shown the 
%relevance of the latter aspect for reaching higher performance. 
%\end{itemize}

In a next step, we intend to support that users could set 
\texttt{VectorizedArrayType} to \texttt{Number}, which would lead to the usage not 
of \texttt{VectorizedArray<Number, 1>} but of a specialized code-path exploiting 
vectorization within an element~\cite{KronbichlerKormann2019}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances in GPU support}
\label{subsec:gpu}

\begin{itemize}
\item overlapping of computation and communication in the case of CUDA-aware MPI
\end{itemize}

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\item \texttt{step-50}
\item \texttt{step-58}
\item \texttt{step-65} presents \texttt{TransfiniteInterpolationManifold}, a
manifold class that can propagate curved boundary information into the
interior of a computational domain, and \texttt{MappingQCache}, which can sample 
the information of expensive manifolds in the points of a \texttt{MappingQ} and 
cache it for further use.
\item \texttt{step-67} presents an explicit time integrator for the
compressible Euler equations discretized with a high-order discontinuous
Galerkin scheme using the matrix-free infrastructure. Besides the use of
matrix-free evaluators for systems of equations and over-integration, it also
presents \texttt{MatrixFreeOperators::CellwiseInverseMassMatrix}, a fast implementation
of the action of the inverse mass matrix in the DG setting using tensor
products. Furthermore, this tutorial demonstrates the usage of new 
pre and post operations, which can be passed to \texttt{cell\_loop()}, to schedule operations on sections of vectors close 
to the matrix-vector product to increase data locality 
and discusses performance-related aspects.
\item \texttt{step-69}
\item \texttt{step-70}
\end{itemize}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 15 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item The functions:
\begin{itemize}
\item \texttt{DoFHandler::loccaly\_owned\_dofs\_per\_processor()}
\item \texttt{DoFHandler::loccaly\_owned\_mg\_dofs\_per\_processor()}
\end{itemize} have been deprecated. As discussed in Subsection~\ref{subsec:performance}, deal.II does not store information for all processes on all processes processes, but only the local information or the locally-relevant information. Users are asked to construct the global information on their own, e.g. by calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item

% \item The \texttt{VectorView} class was removed. We recommend either copying the
%       vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
% \item The function \texttt{Subscriptor::subscribe()}, used through the
%   \texttt{SmartPointer} class, now requires a pointer to a
%       \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
%       subscribed-to object is still valid.
% \item The \texttt{ConstraintMatrix} class gained a template parameter for the scalar
%       type and was been renamed \texttt{AffineConstraints}. Several methods that
%       take vectors or matrices as arguments,
%       such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
%       now require that all matrix and vector arguments have matching number
%       types.
% \item Similarly, the functions \texttt{create\_mass\_matrix} and
%       \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
%       namespace no longer
%       support matrix and vector objects of different types.
\end{itemize}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 6/05/2019
  Giovanni Alzetta,
  Mathias Anselmann,
  Daniel Appel,
  Alexander Blank,
  Vishal Boddu,
  Benjamin Brands,
  Pi-Yueh Chuang,
  Sambit Das,
  Stefano Dominici,
  Nivesh Dommaraju,
  Niklas Fehn,
  Isuru Fernando,
  Andreas Fink,
  Rene Gassm{\"o}ller,
  Alexander Grayver,
  Joshua Hanophy,
  Logan Harbour,
  Daniel Jodlbauer,
  Stefan Kaessmair,
  Eldar Khattatov,
  Alexander Knieps,
  Uwe K{\"o}cher,
  Kurt Kremitzki,
  Dustin Kumor,
  Damien Lebrun-Grandie,
  Jonathan Matthews,
  Stefan Meggendorfer,
  Pratik Nayak,
  Lei Qiao,
  Ce Qin,
  Reza Rastak,
  Roland Richter,
  Alberto Sartori,
  Svenja Schoeder,
  Sebastian Stark,
  Antoni Vidal,
  Jiaxin Wang,
  Yuxiang Wang,
  Zhuoran Wang.

@@

M.~Maier was partially supported by ARO MURI Award No. W911NF-14-0247.

>>>>

@@

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
%     Thomas C. Clevenger,
%     Denis Davydov,
%     Marc Fehling,
%     Daniel Garcia-Sanchez,
%     Graham Harper,
    Timo Heister,
%     Luca Heltai,
    Martin Kronbichler,
%     Ross Maguire Kynch,
%     Matthias Maier,
%     Jean-Paul Pelteret,
%     Bruno Turcksin,
%     David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

% %
% \author[8]{Luca~Heltai}
% \affil[8]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
%   {\texttt{luca.heltai@sissa.it}}}
%
 \author[9]{Martin~Kronbichler}
 \affil[9]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler@lnm.mw.tum.de}}}
%
% \author[10]{Ross~Maguire~Kynch}
% \affil[10]{Zienkiewicz Centre for Computational Engineering,
%   College of Engineering, Swansea University,
%   Bay Campus, Fabian Way, Swansea SA1 8EN, Wales, UK.
%   {\texttt{rkynch@gmail.com}}}
%
\author[11]{Matthias~Maier}
\affil[11]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}
%
% \author[4]{Jean-Paul~Pelteret}
%
% \author[*1]{Bruno~Turcksin}
%
% \author[12]{David Wells}
% \affil[12]{Department of Mathematics, University of North Carolina,
%   Chapel Hill, NC 27516, USA.
%   {\texttt{drwells@email.unc.edu}}}

@@

@@

In addition, there are seven new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\item \texttt{step-50}
\item \texttt{step-58}
\item \texttt{step-65}
\item \texttt{step-67}
\item \texttt{step-69}
\item \texttt{step-70}
\end{itemize}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 15 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item
% \item The \texttt{VectorView} class was removed. We recommend either copying the
%       vector subset into a \texttt{Vector} or using a \texttt{BlockVector}.
% \item The function \texttt{Subscriptor::subscribe()}, used through the
%   \texttt{SmartPointer} class, now requires a pointer to a
%       \texttt{std::atomic<bool>} that tracks whether or not the pointer to the
%       subscribed-to object is still valid.
% \item The \texttt{ConstraintMatrix} class gained a template parameter for the scalar
%       type and was been renamed \texttt{AffineConstraints}. Several methods that
%       take vectors or matrices as arguments,
%       such as \texttt{AffineConstraints::distribute\_local\_to\_global()},
%       now require that all matrix and vector arguments have matching number
%       types.
% \item Similarly, the functions \texttt{create\_mass\_matrix} and
%       \texttt{create\_boundary\_mass\_matrix} in the \texttt{MatrixCreator}
%       namespace no longer
%       support matrix and vector objects of different types.
\end{itemize}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 5/11/2020 MM - TODO: remove authors of paper
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Graham Harper,
Nicole Hayes,
Bang He,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Alexander Knieps,
Martin Kronbichler,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Jan Philipp Thiele,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Doug Shi-Dong,
Natasha S. Sharma,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Mario Zepeda Aguilar,
Wenjuan Zhang.

@@

M.~Maier was partially supported by ARO MURI Award No. W911NF-14-0247 and
NSF Award DMS-1912847.
